Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-13 robdml.tex
pp7

\noindent\textbf{II. Gradual Adversary.}
%
As discussed in \cref{sec:32},  HM[$\mathcal{S},\mathcal{M}$] may still
suffer from the imbalance between learning the embeddings and gaining
adversarial robustness.
%
Hence, we conduct further experiments %with an improved $H_\mathsf{D}$
following the discussion, as shown in \cref{tab:gaeff} and \cref{fig:gaeff}.
%
Compared to HM[$\mathcal{S},\mathcal{M}$], slightly boosting the hardness
training with $g_\mathsf{B}(\cdot)$ where $\xi{=}0.1$ benefits the ERS, but
results in a notably lower R@1;
%
A constant $H_\mathsf{D}$ at the upper bound of Semihard (\ie, $0$; too high
for both the early and the late phase of training) renders model collapse;
%
$H_\mathsf{D}$ at the lower bound (\ie, $-\gamma$; too low for the late phase)
leads to insignificant ERS improvement;
%
$H_\mathsf{D}{=}-\gamma/2$ provides a balance in training objectives, but
still suffers from inflexibility.
%
In contrast, being not susceptible to the mentioned problems of other choices,
HM[$\mathcal{S},g_\mathsf{LGA}$] achieves an ERS on par with
HM[$\mathcal{S},\mathcal{M}$], but is at the lowest R@1 performance penalty among all choices.

>>>>

\noindent\textbf{II. Gradual Adversary.}
%
HM[$\mathcal{S},\mathcal{M}$] may still
suffer from the imbalance between learning the embeddings and gaining
adversarial robustness as discussed in \cref{sec:32}.
%
Hence, we conduct further experiments %with an improved $H_\mathsf{D}$
following the discussion, as shown in \cref{tab:gaeff} and \cref{fig:gaeff}.
%
Compared to HM[$\mathcal{S},\mathcal{M}$], slightly boosting the hardness
training with $g_\mathsf{B}(\cdot)$ where $\xi{=}0.1$ benefits the ERS, but
results in a notably lower R@1;
%
A constant $H_\mathsf{D}$ at the upper bound of Semihard (\ie, $0$; too high
for both the early and the late phase of training) renders model collapse;
%
$H_\mathsf{D}$ at the lower bound (\ie, $-\gamma$; too low for the late phase)
leads to insignificant ERS improvement;
%
$H_\mathsf{D}{=}-\gamma/2$ provides a balance in training objectives, but
still suffers from inflexibility.
%
In contrast, being not susceptible to the mentioned problems of other choices,
HM[$\mathcal{S},g_\mathsf{LGA}$] achieves an ERS on par with
HM[$\mathcal{S},\mathcal{M}$], but is at the lowest R@1 performance penalty among all choices.
